### 2023-12-17 thesis/chapters/03-design.tex
Statistical tests and boxplots

\textbf{A specimen waveform} is picked from each fault class to illustrate their superficial differences. Recordings are filtered to get one of the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz)  to see the patterns most pronounced. The baseline class sample is chosen according to fixed rotor speed.

\subsection{Signal filters}
The DC component in the three-dimensional vibration signal is removed by subtracting the global mean. Immediately follows a digital IIR Butterworth \textbf{ low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Temporal domain waveforms}
        \label{fig:design:fault-temporal-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectra in radial direction}
        \label{fig:design:fault-spectral-waveform}
    \end{subfigure} 
    \caption{Signals for each fault category with the highest fault severity at 2500 rpm}
\end{figure}

@@

\subsection{Statistical tests}
%TODO boxplot in featue selection
%TODO images of machines
%TODO

\subsection{Feature extraction}

@@

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrllll}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Fault}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} &                               &                               &                               &                               \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                   & \multicolumn{1}{r|}{16 (3\%)}                              & \multicolumn{1}{r|}{16 (3\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                 & \multicolumn{1}{r|}{173 (34\%)}                            & \multicolumn{1}{r|}{173 (36\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                 & \multicolumn{1}{r|}{118 (23\%)}                            & \multicolumn{1}{r|}{118 (25\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{67 (13\%)}                             & \multicolumn{1}{r|}{69 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                 & \multicolumn{1}{r|}{61 (12\%)}                             & \multicolumn{1}{r|}{34 (7\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{69 (14\%)}                             & \multicolumn{1}{r|}{68 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                  & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} \\ \cline{1-5}
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}         
\end{tabular}
\end{table}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrrrrr}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 60\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                     
\end{tabular}
\end{table}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrrrrr}
\cline{1-5}
\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 90\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                     
\end{tabular}
\end{table}

@@

\section{Online kNN model}

@@

\section{Measuments on machinery}
- Machinery
% Enum list

- Sensors

@@

- Preliminary measurements
% Waveforms

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
    \end{subfigure} 
    \caption{Signals at 5 s timestamp}
\end{figure}

@@

\section{Data preparation}

- \textbf{Measurements-SHC3.html}
- \textbf{BVS-Measurements.html}

\section{Feature relevance}
- \textbf{FeatureSummary.html}

- choose 3 features
- supervised
	- highly correlated features >= 0.9:
		- Temporal domain (A)
			- std, rms, 1.000000
			- margin, impulse, 0.999079
			- crest, impulse, 0.996807
			- crest, margin,	0.992548
			- pp, max, 0.970055
			- max, (std, rms), 0.938198
			- pp, (std, rms), 0.938180 / 0.928
		- Spectral domain (A)
			- same feature in different window sizes (0.99)
			- kurtosis, skewness, 0.980618
			- std, energy, 0.960110
			- entropy, noisiness, 0.945514

	- calcultate euclidian measure of feature 
	- correlation point biserial, fisher, mutual information
		- Sperman rank correlation: corr, f\_stat, 0.98
	- calculate feature rank
		- Temporal (A) - Remove corr: pp, skewness, margin
		- Spectral (A) - multiple window sizes 
			- (energy, roll off, std)

- online learning features
	- evolution of feature importace

\section{Nearest neighbour classifier}
- \textbf{kNN.html}
- kNN (fault and anomaly)
	- Offine (baseline)
	- Online (evolution)
- parameters: k-neigh, distance
- metrics: accuracy, precision, recall

\section{Clustering}
- Density based clustering
	- DBSCAN (all features, PCA, subset of best)
	- DenStream (all features, subset of best)

\section{Novelty detection}
- Offline (Isolation forest)
- Online (Half-space Tree)

>>>>

\textbf{One specimen waveform} is picked from each fault class to illustrate their superficial differences. Recordings are filtered to get the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz)  to see the patterns most pronounced. The baseline class sample is chosen according to fixed rotor speed.

\subsection{Signal filters}
The DC component in the three-dimensional vibration signal is removed by subtracting the global mean. Immediately follows a digital IIR Butterworth \textbf{low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Temporal domain waveforms}
        \label{fig:design:fault-temporal-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectra in radial direction}
        \label{fig:design:fault-spectral-waveform}
    \end{subfigure} 
    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
\end{figure}

@@

\subsection{Statistical tests}
The statistical tests and visual checks are conducted to assess \textbf{normality and stationary} of time series. Half a second of amplitude samples are used from every sensor channel. These 25 thousand observations are downsampled tenfold to $2500$ points.

\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from normal distribution under most circumstances. The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms. \textbf{Quantile–quantile plots} confirm non-normal distribution because of the striking samples tilt to the diagonal line.

\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root 
(${p < 0.001}$). The same is confirmed with the \textbf{autocorrelation} function shape. It denotes that the stochastic process is stationary as oscillation is bounded.

\subsection{Feature extraction}
% tsfel, scipy

%A) **Activity diagram** (Image)
%1. Label recording using filename path in zip: fault, severity, seq
%2. Split each recording to 5 parts (1 second - 50000 samples)
%3. Calculate rpm (out of impulse tachometer = prominence=3, width=50, 60 / $\Delta t$)
%4. Remove mean - DC component filter
%5. Filter frequencies: cutoff = 10 kHz (Butterworth lowpass filter of 5 order) - peak 20 kHz (not possibe to capture)
%6. Label with 6 classes of faults, and 2 anomaly classes (based on arbitrary severity 0.6 and 0.9)
%7. X - extract temporal features in all axis for both bearings A, B: ax/ay/az_feature_name
%8. X - window size: windows and welch averaging (2**14 = 16384 samples, 3 okná, 3.05 Hz resolution)

%B) **Counts of classes** (to table and Sum) - **Unbalanced dataset**  (2 Tables - `RPM unlimited | RPM limited`)

%C) **Correlation of features with rpm**:
%    - Temporal: mostly **very low** (25% - 75% quantile: 0.07 - 0.20,
%    - Spectral: mostly **very low** for all 5 window sizes: 25% (0.08)  - 75% (0.23)

%C) **Correlation among features**:
%- Feature correlations (> 0.95):
%    - Temporal:
%        - std, rms: 1.0
%        - std, pp, rms, 0.96
%        - pp, max, 0.98
%        - crest, margin, implulse, 0.99
%    - Spectral:
%        - skewness, kurtosis, 0.98

@@

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{rrrrrllll}
\cline{1-3}
\multicolumn{1}{|l|}{\textbf{Fault}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                    \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                  \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                  \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                  \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}

\multicolumn{1}{|l|}{\textbf{Anomaly 60\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}          \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}          \\ \cline{1-3}

\multicolumn{1}{|l|}{\textbf{Anomaly 90\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{1227 (85\%)}                 & \multicolumn{1}{r|}{1197 (86\%)}         \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{211 (15\%)}                 & \multicolumn{1}{r|}{196 (14\%)}         \\ \cline{1-3}
\multicolumn{1}{|r|}{\textbf{Total}}                                                                            & \multicolumn{1}{r|}{\textbf{1438} (100\%)}                       & \multicolumn{1}{r|}{\textbf{1393} (100\%)}               \\ \cline{1-3}
\end{tabular}
\caption{Class count in all rotational speeds}
\end{table}

\subsection{Data volume savings}
%TODO - reduction in data goodput (without metadata): data kept ratio = (nfeat * dim) / (ch * fs * t)
% - (21 * 3) / (3 * 25000 * 1)  (realistic fs because of low pass, we could dowsample by the factor 2) (inverse ratio is data reduction factor =  11904 times less)
% - 7 times less features: (3*3) / (25000*1*3) (83333 times less than original)

% parameters for measurements
% 1. number of measurement places (bearings) -- number of machines * places
% 2. sampling frequency (fs) = const
% 3. interval between measuremnts (s) 
% 4. duration of measuremnt (s)

% Requiremnts classic per bearing (per year): 5s * 20khz * 3dim (365 * 24 = every hour) = (sample is 4/8B just multiplication factor) =  300 kS per measuremnts * 8760 measuremnts = 2.628 GSamples per year per placement
% Frequncy spectra with 1 Hz res = 1*10kHz*3= 30kS = 262.8 MSamples
% All features = 9S  => 78.84 KSamples / year (per year as much as per 3 spectra measurements)

% According to standars is rms velocity enough => indicator of fault (but not of the type)

\section{Nearest neighbour classifier}

\subsection{Batch model}

@@

\subsection{Online kNN model}

@@

\section{Vibration measurement plan}

\subsection{Machinery}
% Enum list

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=0.5\textwidth]{assets/design/machine-fan.jpg}
        \caption{Stand fan Kalorik}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=0.5\textwidth]{assets/design/machine-compressor.jpg}
        \caption{Scroll compressor Copeland}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
        \caption{Water pump KSB Omega}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
        \caption{Water pump Sigma}
    \end{subfigure}
    \caption{Machine}
\end{figure}

\subsection{Sensors}

@@

@@

\subsection{Preliminary measurements}
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
    \end{subfigure} 
    \caption{Signals at 5 s timestamp}
\end{figure}

@@
